---
title: "Get started"
output: 
  bookdown::html_document2:
    number_sections: false
    toc: true
    toc_float:
      toc_collapsed: true
    theme: united
vignette: >
  %\VignetteIndexEntry{UW BIOST561 get started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Function 1: generate partial clique

Generate a random adjacency matrix with a dense partial clique

```{r, include = T}

library(UWBiost561)
set.seed(10)
n_ = 10
clique_fraction_ = .5
clique_edge_density_ = .9

output = generate_partial_clique(n_,clique_fraction_,clique_edge_density_)
output$adj_mat
```


# Function 2: compute_maximal_partial_clique

Compute maximal partial clique

```{r , include = T}
set.seed(10)

n_ = 10
clique_fraction_ = .5
clique_edge_density_ = .9

adj_mat_ = generate_partial_clique(n_,clique_fraction_,clique_edge_density_)$adj_mat
alpha_ = .6

output2 = compute_maximal_partial_clique(adj_mat_, alpha_)

output2$clique_idx
```


# Function 3: compute_maximal_partial_clique_master

This function runs a implementation (dictated by number) using the inputs adj_mat and alpha. For example, compute_maximal_partial_clique_master(adj_mat, alpha, number = 5) executes compute_maximal_partial_clique5(adj_mat, alpha).

```{r, include = T}
set.seed(10)

n_ = 10
clique_fraction_ = .5
clique_edge_density_ = .9


adj_mat2 = generate_partial_clique(n_,clique_fraction_,clique_edge_density_)$adj_mat
alpha2 = .6
number2 = 5

output3 = compute_maximal_partial_clique_master(adj_mat2, alpha2, number2)
output3$clique_idx

```
